Dynamic Transition Analysis with TIMES

### 2020-06-23 doc/2020-03-paper/discussion.tex
added results details
Former-commit-id: ed19f4a90ca89ba623e169f45f26da001cb413db
Former-commit-id: d18cad00c2db357dbb0f67988ccf31fec6140bba

\section{Discussion}
% This should explore the significance of the results of the work, not repeat
% them. A combined Results and Discussion section is often appropriate. Avoid
% extensive citations and discussion of published literature.

>>>>

\section{Discussion}
% This should explore the significance of the results of the work, not repeat
% them. A combined Results and Discussion section is often appropriate. Avoid
% extensive citations and discussion of published literature.
Notes for Ansh:
Importance of nuclear : cost of various transitions, flexibility by itself and when coupled with storage (Li-ion, H2). How it precludes the need for CCS.
Urgency of transition : scenarios + sensitivity analysis.
Li-ion storage: land use requirements for each case, qualitatively discuss Co, Ni requirements.
AECs,PEMECs,SOECs need to be highly flexible with high availability factors.
SOFCs: need for extremely responsive SOFCs with high availability factor, flexible operation (cite challenges from NREL).

### 2020-06-23 doc/2020-03-paper/methods.tex
added results details
Former-commit-id: ed19f4a90ca89ba623e169f45f26da001cb413db
Former-commit-id: d18cad00c2db357dbb0f67988ccf31fec6140bba

While electricity demand in the near term is expected to grow, long term electricity demand is expected to plateau, or even decrease, due to Japan's aging population. However, precisely quantifying this rate of decrease is challenging as there is potential for increased electrification of  transportation and industrial sectors. Hence, post-2030, we have assumed a demand curve based on the likelihood of increased electrification resulting in increasing demand for electricity, but the demand eventually plateaus due to the aging population. The unique initial condition of the post-Fukushima Japanese electricity supply system is captured using \gls{EDMC} data from 2013-2016. Long term impacts of factors such as the retirement of the existing nuclear fleet and the new deployment of emerging, potentially disruptive technology is assessed by simulating the system until 2100. The carbon cost of each technology is accounted for using an emission coefficient that incorporates both direct emissions and life cycle emissions (averaged over the entire lifetime output) for every technology, as applicable.

@@

\begin{table}[!ht]
	\caption{CO$_2$ constraints.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.1\textwidth} p{0.22\textwidth}p{0.16\textwidth} p{0.4\textwidth}}
		\hline
\textbf{Year} & \textbf{Emission limit} & \textbf{Base Year} & \textbf{Reduction from base year} \\
\hline
2030 & 438 Mt CO$_2$-eq. & 2013 & 26 \% \\
2050 & 75 Mt CO$_2$-eq. & 1990 & 80 \% \\
2100 & 75 Mt CO$_2$-eq. & 1990 & 80 \% \\
\hline 
	\end{tabularx}
\label{co2-limits}
\end{table}

@@

>>>>

While electricity demand in the near term is expected to grow, long term electricity demand is expected to plateau, or even decrease, due to Japan's aging population. However, precisely quantifying this rate of decrease is challenging as there is potential for increased electrification of  transportation and industrial sectors. Hence, post-2030, we have assumed a demand curve based on the likelihood of increased electrification resulting in increasing demand for electricity, but the demand eventually plateaus due to the aging population. The unique initial condition of the post-Fukushima Japanese electricity supply system is captured using \gls{EDMC} data from 2013-2016. Long term impacts of factors such as the retirement of the existing nuclear fleet and the new deployment of emerging, potentially disruptive technology is assessed by simulating the system until 2100. The carbon cost of each technology is accounted for using an emission coefficient that incorporates both direct emissions and life cycle emissions (averaged over the entire lifetime output) for every technology, as applicable. The daily and seasonal variability of renewables is incorporated using day-night and seasonal time periods. The availability of renewables varies during these time periods (for instance, solar output drops to zero at night, and a similar notion of days without wind is incorporated) based on the annually averaged capacity factors of renewables in Japan (cite).

@@

\begin{table}[!ht]
	\caption{CO$_2$ constraints.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.1\textwidth} p{0.22\textwidth}p{0.16\textwidth} p{0.4\textwidth}}
		\hline
\textbf{Year} & \textbf{Emission limit} & \textbf{Base Year} & \textbf{Reduction from base year} \\
\hline
2030 & 438 Mt CO$_2$-eq. & 2013 & 26 \% \\
2050 & 75 Mt CO$_2$-eq. & 1990 & 80 \% \\
2100 & 75 Mt CO$_2$-eq. & 2050 & 0 \% \\
\hline 
	\end{tabularx}
\label{co2-limits}
\end{table}

@@

All lithium ion storage has an energy-to-power ratio of 4 (cite NREL), a discharge time of 4h, and an availability factor of about 96\%(based on 3500 lifetime cycles over 10 years). Our assumptions about the reduction in the investment costs of life-cycle emissions are conservative due to the rising cost of cobalt and nickel and the manufacture of lithium-ion batteries in high \gls{GHG} emission countries. All hydrogen storage devices are operated with a maximum availability factor of 90\%, making them extremely flexible for load following. Long-term storage of hydrogen is also available using hydrogen tanks with appropriate losses (cite IEA). For hydrogen electrolyzers and fuel cells, life-cycle emissions from just the stack are considered, as \gls{BOP} emissions from utility scale hydrogen depend strongly on the nature of the hydrogen facility and the source of energy used for electrolysis (eg: wind, biomass, solar photovoltaic etc.)

### 2020-06-23 doc/2020-03-paper/results.tex
added results
Former-commit-id: 4c3b33b13ba2639f7649dce115d0832e5f3badac
Former-commit-id: 5c0328da46f31d8f48794b2dba882d21e6c30d7b
section 3 added parameter details, added section 5 notes
Former-commit-id: 3c3e5fdaddb8f4d18f3fe5b84bec77119d161dcf
Former-commit-id: fd5392759009fc1b04c95f5123799685cb74ee9b
added results details
Former-commit-id: ed19f4a90ca89ba623e169f45f26da001cb413db
Former-commit-id: d18cad00c2db357dbb0f67988ccf31fec6140bba

\section{Results and discussion} \label{Results-and-discussion}
RESULTS

>>>>

\section{Results} \label{Results-and-discussion}
\subsection{Transition Scenarios}
Notes for Ansh: electricity diverted to storage could be reduced to text with percentages i.e. "total amount of electricity diverted to storage=, electricity for storage came from nuclear (50\%), solar(30\%),wind(20\%) over 2017-2100". Same for H2 (total GWh generated, amount).

Scenario 1 results (fig. \ref{scen1}) demonstrate our model's attempt at decarbonization using existing technologies without deploying new nuclear power. Under these conditions, coal and oil must be retired by 2030, and natural gas by 2050. All existing nuclear power plants must restarted by <YEAR> at full operating capacity. With renewable energy as the only option for decarbonization, significant investments in solar, onshore wind, offshore wind (both fixed-bottom and floating), and lithium ion storage are necessary. The presence of a large share of renewables results in significant overgeneration of electricity during some years. Due to reduced flexibility caused by the retirement of natural gas and an increase in the share of renewables, nuclear power plants must be able to load follow, which is simulated in our model. The plot displaying the electricity supplied to the end-user shows a high degree of variability as excess electricity from renewables, hydropower, and nuclear power is often diverted to lithium-ion storage as appropriate, instead of being directly supplied to the \gls{TIMES} process. Despite the deployment of a large amount of renewables, the model fails to achieve the 2030 and 2050 emission reduction goals by <AMT1> and <AMT2> respectively. Furthermore, emissions continue to rise after 2050 primarily due to life-cycle emissions of lithium-ion batteries. The total cost of this transition is \textbf{insert number here.}

With the option of deploying new nuclear reactors available in Scenario 2 (fig. \ref{scen2}) , the model chooses to rapidly deploy nuclear power plants at the maximum allowed growth rate despite the high investment cost of nuclear, due to its low life-cycle emissions. Coal and oil are again retired rapidly, but due to the reduction in emissions by nuclear power, natural gas power plants can continue to operate. The amount of renewables required for decarbonization is reduced dramatically. This combined with the load following capabilities of natural gas plants and nuclear reactors drastically reduces the amount of lithium ion storage. The model is able to achieve its 2030 and 2050 decarbonization goals, and automatically decarbonizes more than the required limit by 2100. The total transition cost is \textbf{insert number here.}
\begin{figure}[h] 
\centering
\label{scen1}
\includegraphics[scale=0.25]{figures/conv_nonuc}
\caption{Conventional technologies, no new nuclear.}
\end{figure}

\begin{figure}[h] 
\centering
\label{scen2}
\includegraphics[scale=0.25]{figures/conv_nuc}
\caption{Conventional technologies, with new nuclear.}
\end{figure}

\begin{figure}[h] 
\centering
\label{scen3}
\includegraphics[scale=0.2]{figures/newtechs_nonuc}
\caption{Emerging technologies, no new nuclear.}
\end{figure}

\begin{figure}[h] 
\centering
\label{scen4}
\includegraphics[scale=0.2]{figures/newtechs_nuc}
\caption{Emerging technologies, no new nuclear.}
\end{figure}

\subsection{Sensitivity analysis}
